An open source scientific article

### 2022-07-12 src/tex/ms.tex
migrate to showyourwork v0.3.0
line endings
[showyourwork] dummy change
[showyourwork] overleaf sync
Add missing \script{} command
Need to add \script{} now within figure environments for showyourwork to run the figure script.
[showyourwork] resolve overleaf conflict

% Filler text
\usepackage{blindtext}

@@

% Author list
\author[0000-0000-0000-0000]{First Author}

% Abstract with filler text
\begin{abstract}
    \blindtext
\end{abstract}

% Main body with filler text
\section{Introduction}
\Blindtext[4]

\section{Methods}

\subsection{Accuracy of astroNN}

@@

\subsection{Measurements of the Type Ia Supernova Delay Time Distribution}

@@

>>>>

% showyourwork!
\usepackage{showyourwork}

@@

% Author list
\author[0000-0003-3781-0747]{Liam O. Dubay}

% Abstract with filler text
\begin{abstract}
    Abstract.
\end{abstract}

% Main body with filler text
\section{Introduction}

\section{Methods}
\label{sec:methods}

\subsection{Accuracy of astroNN}
\label{subsec:astronn-quality}

@@

\subsection{Measurements of the Type Ia Supernova Delay Time Distribution}
\label{subsec:dtd-measurements}

\begin{figure}
    \centering
    \includegraphics{figures/delay_time_distributions.pdf}
    \caption{Delay time distribution functions}
    \label{fig:dtds}
    \script{delay_time_distributions.py}
\end{figure}

@@

\section{Results}
\label{sec:results}

\subsection{One-Zone Models}
\label{subsec:onezone-results}

\subsubsection{The SN Ia Delay-Time Distribution}

Adjusting the parameters of the DTD affects how steeply the abundance track in [Fe/H]-[O/Fe] space falls from its initial ``plateau'' and the location of the ``knee.'' Figure \ref{fig:onezone-slope-timescale} shows abundance tracks from one-zone models which assume different slopes of a power-law DTD or different timescales of an exponential DTD. A steeper power-law slope results in a steeper decline in [O/Fe] and a lower knee, as does a shorter exponential timescale. The consequence is that a very shallow power-law produces similar observable signatures to a very steep exponential, which suggests these models may be difficult to distinguish in this parameter space.

\begin{figure}
    \centering
    \includegraphics{figures/onezone_slope_timescale.pdf}
    \caption{\textit{Center:} Abundance tracks in the [Fe/H]-[O/Fe] plane for one-zone models with various DTD parameters. Tracks from models which assume a power-law DTD are in black, with dotted, dashed, and solid curves representing power-law slopes ($\alpha$) of $-0.8$, $-1.1$, and $-1.4$, respectively. Tracks from models which assume an exponential DTD are in purple, with dotted, dashed, and solid curves representing exponential decay timescales ($\tau$) of 1.5 Gyr, 3 Gyr, and 6 Gyr, respectively. \textit{Top:} MDFs generated from by one-zone models. \textit{Right:} Distribution of [O/Fe] generated by the one-zone models.}
    \label{fig:onezone-slope-timescale}
    \script{onezone_slope_timescacle.py}
\end{figure}

\subsubsection{The Minimum SN Ia Delay Time}

Figure \ref{fig:onezone-dtd-delay} shows that the minimum SN Ia delay time has a much stronger effect on the abundance track and MDFs of models which assume a power-law DTD than models which assume an exponential, due to the much higher SN Ia rate in the power-law models at early times (see Figure \ref{fig:dtds}). Moreover, a power-law DTD with a long minimum delay may be observationally hard to distinguish from an exponential.

\begin{figure}
    \centering
    \includegraphics{figures/onezone_dtd_delay.pdf}
    \caption{Similar to Figure \ref{fig:onezone-slope-timescale} but with varying minimum SN Ia delay time ($t_D$). Dashed curves represent models with a minimum delay time of 40 Myr, while solid curves represent models with a minimum delay time of 150 Myr. The black curves represent a power-law DTD with a slope of $-1.1$, while the purple curves represent an exponential DTD with a timescale of 1.5 Gyr.}
    \label{fig:onezone-dtd-delay}
    \script{onezone_dtd_delay.py}
\end{figure}

\subsubsection{The Star Formation History}

Figure \ref{fig:onezone-delay-taustar} shows results from one-zone models with a power-law DTD which differ in their assumed minimum SN Ia delay time ($t_D$) or star formation efficiency timescale ($\tau_*$). In [Fe/H]-[O/Fe] space, doubling or halving the minimum delay time produces similar results to doubling or halving the SFE timescale. A shorter minimum delay time means SNe Ia will start to explode sooner after the star formation burst, giving less time for CCSNe to explode at the plateau of the abundance track. Similarly, a longer SFE timescale means fewer massive stars will be produced by the initial star formation burst, resulting in fewer CCSNe before the first SNe Ia explode.

These parameters have similar effects on the abundance tracks but very different effects on the MDFs. Altering the SFE timescale changes the stellar distribution of [Fe/H], especially at the low-metallicity end, as shown in the top panel of Figure \ref{fig:onezone-delay-taustar}. However, as a change in the SFE timescale affects both the number of high-mass and low-mass stars produced, it does not affect the distribution of [O/Fe], as shown in the right-hand panel of Figure \ref{fig:onezone-delay-taustar}. Meanwhile, a change in the minimum SN Ia delay time does not impact the total number of SNe which explode, so the distribution of [Fe/H] is largely unaffected, while it does result in a change in the number of high-$\alpha$ stars formed and therefore the distribution of [O/Fe].

\begin{figure}
    \centering
    \includegraphics{figures/onezone_delay_taustar.pdf}
    \caption{Similar to Figure \ref{fig:onezone-slope-timescale} but with varying minimum SN Ia delay time ($t_D$) and star formation efficiency timescale ($\tau_*$). Tracks with $\tau_*=2$ Gyr are represented in black, while a track with a shorter $\tau_*=1$ Gyr is shown in red and a track with a longer $\tau_*=4$ Gyr is in yellow. The dotted, solid, and dashed black curves represent a minimum delay time of 40 Myr, 80 Myr, and 160 Myr, respectively. A power-law DTD is assumed in all models.}
    \label{fig:onezone-delay-taustar}
    \script{onezone_delay_taustar.py}
\end{figure}

\pagebreak
